\documentclass[11pt,a4paper]{article}

% Packages for better formatting
\usepackage{geometry}
\usepackage{setspace}
\usepackage{hyperref}

% Page margins
\geometry{margin=1in}

% Line spacing
\setstretch{1.15}

\begin{document}

\begin{center}
\textbf{Nina Zhang}\\
Email: ninazeng@umich.edu\\
Phone: (646) 648-7593\\
Website: https://zemaye.net\\
GitHub: https://github.com/zemaye1
\end{center}

\vspace{0.5in}

Dear Hiring Manager,

\vspace{0.3in}

Studying under Dr. David Rosenberg, I created with a team of three, a lambdaMART ranking engine for recommending stack overflow question answer pairs to match a query. We presented our findings to the CTO Vladimir. Dr. Rosenberg teaches the ML 101 class at NYU. Our advisor during this time was Amanda Stent who has many citations for her NLP oeuvre. They helped come up with the idea of comparing sentence vector similarities. We made our own set of data by labelling question answer pairs.

\vspace{0.2in}

With experience building apps using flask and django and experience working on the premiere financial distributed backends at intercontinental exchange and at the Bloomberg terminal, I can apply CAP theorem and distributed systems principles to any idea startup or more established market products. I excel in creating dev environments that are stable writing Perl scripts which automate developer experience to be a smooth and comfortable experience producing binaries that are tagged with standard build scripts. I specialise in high throughput c++ systems where information is coming in from multiple sources and distributed into databases or multiplexed into client terminals. The distributed systems I worked on were primarily entirely in C++ the components in which efficiency was a requirement. For fast implementation, python microservices were preferred.

\vspace{0.2in}

My name is Nina Zhang and I am a full stack developer. I am a libre tech advocate including but not limited to FOSS technologies. I've worked at premiere software fintech companies like Bloomberg and Intercontinental Exchange owner of the New York Stock Exchange. I can talk to distributed systems people, I can talk to applications people, and I can talk to machine learning people. I can identify problems throughout a system and troubleshoot with a wide variety of engineers. I am one of the few people who can identify problems and synergize across a system. My front end experience lies in the blink chromium rendering engine and building the widgets which formulate a UI while reading the C++ underneath and making sure the way one catches events takes advantage of the core C++ optimizations. I work on massively parallel and distributed systems. The system was a chat system and I added support for rich text metadata imbued messages.

\vspace{0.2in}

I studied profiling tools in depth. Comparing helgrind to Thread Sanitizer instrumenting code to find hotspots and carefully changing lock unlock semantics to relieve contention.

\vspace{0.2in}

If you want to create reactive front ends with stable UI implementations capable of supporting and spanning across servers I can do this.

\vspace{0.2in}

I have a degree from the prestigious computer science program at Ann Arbor where I had mentors like Dr. Peter Chen as my advisor who is a seminal figure in security and operating systems. I had Dr. Seth Pettie who taught algorithms for max flow min cut graph problems that may come up.

\vspace{0.2in}

I have also made a cursor app which analyzes a query prelabels the results based on the viewpoint as a chrome extension.

\vspace{0.5in}

Sincerely,\\
Nina Zhang

\end{document}
